---
title: "wyz.code.rdoc"
author: "Fabien GELINEAU"
date: "Last update 2019.08.27"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{wyz.code.rdoc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
body {
text-align: justify}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval = TRUE, echo = FALSE}
pkn <- 'wyz.code.rdoc'
```


Package **`r pkn`** aims to generate **R documentation**(manual pages) directly from
offensive programming instrumentation. 

Read [Offensive programming book](https://neonira.github.io/offensiveProgrammingBook/) to get introduction and advanced knowledge on the topic. Main chapter related to [documentation generation](https://neonira.github.io/offensiveProgrammingBook/generating-r-documentation.html) might be of first interest. 


# Releases 

## 1.1.7

Main improvements are 

1. corrected many typographic errors in i/o with end-user
2. completed unit tests
3. enforced higher code coverage (from 75% up to 99.28%)
4. changed many functions visibility from hidden (internal to package) to visible (end-user available).
5. documentation completion
6. clean up package dependencies. 


This release replaces fully olders ones, that are now considered obsoletes. Keep the pace, and 
upgrade your packages if you do not use this version or a higher one!


